Segmentation Using Attributes

### 2010-05-11 paper.tex
paper with results of add

\begin{table}
\centering
\begin{tabular}{|l|l|l|}
\hline Parameter & recall & prec \\
\hline 0.8,0.4,0.1  & 0.4317 & 0.2393 \\
\hline 0.8,0.4,0.15  & 0.3849 & 0.2370 \\
\hline 0.8,0.6,0.15  & 0.2720 & 0.2501 \\
\hline
\end{tabular}
\caption{Results from the additive algorithm on all car images.
Parameter contains the three threshold, $thre\_perf$, $thre\_pos$
and $thre\_neg$, recall is the object detection recall rate and prec
is the segmentation precision on all detected images.}
\label{table:aresults}
\end{table}

@@

>>>>

\begin{table}
\centering
\begin{tabular}{|l|l|l|}
\hline Methods & Precision(\%) & Recall(\%) \\
\hline LowFea  & 55.97 & 70.96 \\
\hline Att1    & 51.89 & 51.89 \\
\hline Random  & 35.19 & 50.00 \\
\hline Add     & 60.82 & 54.06 \\
\hline
\end{tabular}
\caption{Object classification results of three baseline methods and the proposed additive algorithm.}
\label{table:aresults}
\end{table}

@@

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/add_res/car/2008_007064.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_007171.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000251.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/add_res/car/2008_007064.jpg_1_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000052.jpg_1_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_007171.jpg_1_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000251.jpg_1_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results_car}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000868.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000884.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_001830.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_001867.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000868.jpg_1_bad.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000884.jpg_1_bad.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_001830.jpg_1_bad.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_001867.jpg_1_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results_car}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000021.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001971.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002673.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002138.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000021.jpg_2_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001971.jpg_2_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002673.jpg_2_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002138.jpg_2_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results_car}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000804.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001805.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002358.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_003673.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000804.jpg_2_bad.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001805.jpg_2_okay.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002358.jpg_2_okay.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_003673.jpg_2_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results_car}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001542.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001992.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002172.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002509.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001542.jpg_3_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001992.jpg_3_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002172.jpg_3_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002509.jpg_3_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results_car}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_000403.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002835.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_003055.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_004470.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_000403.jpg_3_bad.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002835.jpg_3_bad.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_003055.jpg_3_okay.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_004470.jpg_3_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results_car}
\end{figure*}
